Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-03 ms.tex
very minor edits

%We have cross-matched DECaLS DR1 and DR2 sources, and selected samples of
%faint WISE detections in DR1 for each band, $5<$ (W? S/N) $<6$. We find that
%in DECaLS DR2, these same sources have on average 1.33$\times$ (1.19$\times$)
%higher S/N in W1 (W2). For comparison, the expectation based purely on
%reduced statistical noise in the WISE imaging is 1.38$\times$ improvement in
%S/N.

To make such a comparison, for each of W1 and W2, we select a sample of DECaLS 
DR2 sources with \verb|type|='PSF', \verb|wise_fracflux|$<$0.1, more than
one DECam observation, and WISE S/N within the range 10$\pm$1. We
then obtain a DR1-DR2 comparison sample by cross-matching these DR2 objects
with DR1 \verb|type|='PSF' sources, using a 1$''$ matching radius. The resulting
comparison samples have $\sim$415,000 objects. For such
sources, we find median reductions in WISE forced photometry uncertainties
of 1.38$\times$ (1.30$\times$) in W1 (W2). The corresponding median increase in
coverage is 1.9$\times$ in both bands, leading us to expect a factor of 
1.38$\times$ decrease in uncertainties based purely on reduced statistical 
noise.

>>>>

To make such a comparison, for each of W1 and W2, we select a sample of 
isolated DECaLS DR2 sources with \verb|type|=`PSF', \verb|wise_fracflux|$<$0.1,
more than one DECam observation, and WISE S/N within the range 10$\pm$1. We
then obtain a DR1-DR2 comparison sample by cross-matching these DR2 objects
with DR1 \verb|type|=`PSF' sources, using a 1$''$ matching radius. The resulting
comparison samples have $\sim$415,000 objects. For such
sources, we find median reductions in WISE forced photometry uncertainties
of 1.38$\times$ (1.30$\times$) in W1 (W2). The corresponding median increase in
coverage is 1.9$\times$ in both bands, leading us to expect a factor of 
1.38$\times$ decrease in uncertainties based purely on reduced statistical 
noise.
